### 2013-06-15 ms_V3.tex

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{color,lineno,setspace,graphicx,multirow,kpfonts}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes]{biblatex}
\bibliography{./library, EKLOF,CHEUNG,THUILLER,CANARD, POISOT, WILLIAMS, HAVENS, BAISER, PEREIRA, WHITEHEAD, STOUFFER, STOU2, ALLESINA, ALLOUCHE, ALBOUY, FROESE, JACKSON}
%\bibliograph{library}

@@

%------------------------------------------------------------
\section{Introduction}
One of the current challenges in ecology is to predict the emergence and re-assembly of communities following species responses to global changes. Understanding this is made all the more important as these emergent ecosystems will be more common with increasing human pressure. We know that species invasions, biomass harvesting, ranges shifts, disturbances and changes in land use are important drivers of biodiversity turnover. How they affect species composition is now well described \parencite{Pereira2010}, but forecasting their impact on community structure and functioning requires \emph{a priori} knowledge of potential interactions among species. Predicting interactions among species that never co-occurred proves challenging, as traditional empirical methods of food web sampling such as stomacal content analysis cannot be applied. While for competitive communities this task could be achieved using predictive modeling based on functional traits \parencite{McGill2006, Albouy2010} or phylogeny \parencite{Cavender-Bares2009, Mouquet2012} , it is much more difficult to forecast trophic interactions in a food web \parencite{Ings2009, Tylianakis2008,Montoya2010}.

Inferring potential interactions among species of an arbitrary defined pool is a major step to predict the structure of emergent communities and their functioning. We call these potential interactions among species from a regional pool the \emph{metaweb} \parencite{Dunne2006}. A metaweb takes the form of an adjacency matrix $\mathbf{M}$, of size $s\times s$ for a pool of $s$ species, and in which $\mathbf{M_{ij}} = 1$ if species $i$ can consume species $j$, and $0$ otherwise. This matrix aggregates the trophic interactions among all species from the pool that are susceptible to both co-occur and interact at the regional scale \parencite{Dunne2006}. With a metaweb in hands, one could analyze the impacts of global changes, such as range shifts or species invasions, on the potential community structure, by extracting the relevant species and examining the properties of the community they define. While this concept is progressively finding its way through theoretical spatial food web ecology \parencite{Lafferty2010, Pillai2009, Gravel2011a, Gravel2011b}, it is still limited by data availability and predictive accuracy. Published metaweb data rely on literature surveys \parencite{Havens1992, Piechnik2008, Baiser2012}, or a compilation of several local food webs \parencite{Stanko2002, Poisot2012a}, making them resolved only for species that co-occurred a large enough number of times.

@@

The method aims to infer the potential interactions among a pool of species from a subset of observations of predator-prey interactions. The method follows the following steps, with details provided below: 
\begin{itemize}
\item[Step 1:] Log transformation of the body size data;
\item[Step 2:] Statistical analysis of the predator-prey body size relationship;
\item[Step 3:] Inferrence of the niche model parameters for all species from the species pool;
\item[Step 4:] Interpretation of the parameters and computation of the metaweb.
\end{itemize}
We also provide an example of R code (R Core Development Team) and data in the Supplementary Material, detailling the step by step procedure and the format of the input data.

@@

Assuming that body size is the main niche axis structuring trophic interactions,
the parameter $n_i$ corresponds simply to the log of body size (in mass or
length) of species $i$. Though only the relative position of all species along
the body size gradient needs to be respected, it is possible to standardize log
body size values between 0 (minimum size in the regional species pool) and 1
(maximal size). We then consider a linear relationship between the decimal
logarithm of body size and the centroid of the niche (the dark line at Fig. 1).
This relationship is obtained by fitting the linear model $c =
\mathrm{log}_{10}(B_{prey})=\alpha_0 +
\alpha_1\times\mathrm{log}_{10}(B_{pred})$ to the data, where $B_{prey}$ and
$B_{pred}$ are the prey and predator body size respectively. The lower and upper
boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
quantile regressions between $\mathrm{log}_{10}(B_{prey})$ and
$\mathrm{log}_{10}(B_{pred})$ (the dotted lines at Fig. 1, see the example at Fig.
2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.  In sum,
the parameter $n_i$ for any species of the metaweb is given by the standardized
value of the log body size $B_i$, $c_i$ is estimated from the linear regression
between predator and prey log body size and $r_i$ from the quantile regressions.

@@

\subsection*{Figure 2}
Example of predator-prey body size relationship and predictions from the parameterized niche model. Black dots represent observed links while open dots are predicted interactions based on the parameterization of the niche model. The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not observation ("b") and an open circle a non-predicted and observed link ("c"). Data from a creek bed located in Australia \parencite{Brose2005}.

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{color,lineno,setspace,graphicx,multirow,kpfonts}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes]{biblatex}
\bibliography{./library, EKLOF,CHEUNG,THUILLER,CANARD, POISOT, WILLIAMS, HAVENS, BAISER, PEREIRA, WHITEHEAD, STOUFFER, STOU2, ALLESINA, ALLOUCHE, ALBOUY, FROESE, JACKSON,STANKO}
%\bibliograph{library}

@@

%------------------------------------------------------------
\section{Introduction}
One of the current challenges in ecology is to predict the emergence and re-assembly of communities following species responses to global changes. Understanding this is made all the more important as these novel ecosystems will be more common with increasing human pressure. We know that species invasions, biomass harvesting, ranges shifts, disturbances and changes in land use are important drivers of biodiversity turnover. How they affect species composition is now well described \parencite{Pereira2010}, but forecasting their impact on community structure and functioning requires \emph{a priori} knowledge of potential interactions among species. Predicting interactions among species that never co-occurred proves challenging, as traditional empirical methods of food web sampling such as stomacal content analysis cannot be applied. While for competitive communities this task could be achieved using predictive modeling based on functional traits \parencite{McGill2006, Albouy2010} or phylogeny \parencite{Cavender-Bares2009, Mouquet2012} , it is much more difficult to forecast trophic interactions in a food web \parencite{Ings2009, Tylianakis2008,Montoya2010}.

Inferring potential interactions among species of an arbitrary defined pool is a major step to predict the structure of emergent communities and their functioning. We call these potential interactions among species from a regional pool the \emph{metaweb} \parencite{Dunne2006}. A metaweb takes the form of an adjacency matrix $\mathbf{MW}$, of size $s\times s$ for a pool of $s$ species, and in which $\mathbf{MW_{ij}} = 1$ if species $i$ can consume species $j$, and $0$ otherwise. This matrix aggregates the trophic interactions among all species from the pool that are susceptible to both co-occur and interact at the regional scale \parencite{Dunne2006}. With a metaweb in hands, one could analyze the impacts of global changes, such as range shifts or species invasions, on the potential community structure, by extracting the relevant species and examining the properties of the community they define. While this concept is progressively finding its way through theoretical spatial food web ecology \parencite{Lafferty2010, Pillai2009, Gravel2011a, Gravel2011b}, it is still limited by data availability and predictive accuracy. Published metaweb data rely on literature surveys \parencite{Havens1992, Piechnik2008, Baiser2012}, or a compilation of several local food webs \parencite{Stanko2002, Poisot2012a}, making them resolved only for species that co-occurred a large enough number of times.

@@

The method aims to infer the potential interactions among a pool of species from a subset of observations of predator-prey interactions. The method follows the following steps, with details provided below: 
\begin{description}
\item[Step 1:] Log transformation of the body size data;
\item[Step 2:] Statistical analysis of the predator-prey body size relationship;
\item[Step 3:] Inferrence of the niche model parameters for all species from the species pool;
\item[Step 4:] Interpretation of the parameters and computation of the metaweb.
\end{description}
We also provide an example of R code (R Core Development Team) and data in the Supplementary Material, detailling the step by step procedure and the format of the input data.

@@

Assuming that body size is the main niche axis structuring trophic interactions,
the parameter $n_i$ corresponds simply to the log of body size (in mass or
length) of species $i$. Though only the relative position of all species along
the body size gradient needs to be respected, it is possible to standardize log
body size values between 0 (minimum size in the regional species pool) and 1
(maximal size). We then consider a linear relationship between the decimal
logarithm of body size and the centroid of the niche (the dark line at Fig. 1).
This relationship is obtained by fitting the linear model $c =
\mathrm{log}_{10}(M_{prey})=\alpha_0 +
\alpha_1\times\mathrm{log}_{10}(M_{pred})$ to the data, where $M_{prey}$ and
$M_{pred}$ are the prey and predator body size respectively. The lower and upper
boundaries of the feeding range are easily obtained by fitting the 5\% and 95\%
quantile regressions between $\mathrm{log}_{10}(M_{prey})$ and
$\mathrm{log}_{10}(M_{pred})$ (the dotted lines at Fig. 1, see the example at Fig.
2). We note them as $r_{low,i}$ and $r_{high,j}$ respectively, and the
corresponding parameters $\beta_{0,low/high}$ and $\beta_{1,low/high}$.  In sum,
the parameter $n_i$ for any species of the metaweb is given by the standardized
value of the log body size $M_i$, $c_i$ is estimated from the linear regression
between predator and prey log body size and $r_i$ from the quantile regressions.

@@

\subsection*{Figure 2}
Example of predator-prey body size relationship and predictions from the parameterized niche model. Open dots represent observed links while black dots are predicted interactions based on the parameterization of the niche model. The bullseye symbols thus correspond to a match between predicted occurrence of a link and the real data (the "a" classification in the calculation of the TSS, see main text), a black dot a predicted link with not observation ("b") and an open circle a non-predicted and observed link ("c"). Data from a creek bed located in Australia \parencite{Brose2005}.
